Add Plant Functional Type (PFT) labels

### 2021-03-30 R/add_plant_functional_type.Rmd
labels added to each genusSpecies category in a lookup table. tagged uncertain PFTs as ???. once verified, need to apply the table to the spectral library

  else if(genusSpecies == ""){
    taxon_pft_lookup$pft[i] = ""
    taxon_pft_lookup$commonName[i] = ""}

  else if(genusSpecies == ""){
    taxon_pft_lookup$pft[i] = ""
    taxon_pft_lookup$commonName[i] = ""}

  else if(genusSpecies == ""){
    taxon_pft_lookup$pft[i] = ""
    taxon_pft_lookup$commonName[i] = ""}

  else if(genusSpecies == ""){
    taxon_pft_lookup$pft[i] = ""
    taxon_pft_lookup$commonName[i] = ""}

  else if(genusSpecies == ""){
    taxon_pft_lookup$pft[i] = ""
    taxon_pft_lookup$commonName[i] = ""}

@@

  else if(genusSpecies == "Rhamnus davurica"){
    taxon_pft_lookup$pft[i] = "???"              # ???
    taxon_pft_lookup$commonName[i] = "Dahurian buckthorn"}

  else print("PFT unknown")

>>>>

  else if(genusSpecies == "Quercus shumardii"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "Shumard's oak"}

  else if(genusSpecies == "Quercus sp."){
    taxon_pft_lookup$pft[i] = "???"  # apparently there are evergreen oak species? 
    taxon_pft_lookup$commonName[i] = "oak"}

  else if(genusSpecies == "Quercus velutina"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "black oak"}

  else if(genusSpecies == "Quercus virginiana"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "live oak"}

  else if(genusSpecies == "Rhamnus davurica"){
    taxon_pft_lookup$pft[i] = "???"     #  spreading shrub or small tree reaching 25 to 30 feet
    taxon_pft_lookup$commonName[i] = "Dahurian buckthorn"}

  else if(genusSpecies == "Rhus aromatica"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "fragrant sumac"}

  else if(genusSpecies == "Rhus glabra"){
    taxon_pft_lookup$pft[i] = "woody_shrub"
    taxon_pft_lookup$commonName[i] = "smooth sumac"}

  else if(genusSpecies == "Sassafras albidum"){
    taxon_pft_lookup$pft[i] = "deciduous_forest" # deciduous shrub or tree. trees are 9 to 18 m
    taxon_pft_lookup$commonName[i] = "sassafras"}

  else if(genusSpecies ==  "Sassafras sp."){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "sassafras"}

  else if(genusSpecies == "Sideroxylon lanuginosum"){
    taxon_pft_lookup$pft[i] = "???" # deciduous multi-trunked tall shrub or medium-sized tree to 48ft or more
    taxon_pft_lookup$commonName[i] = "gum bully"}

  else if(genusSpecies == "Symplocos sp."){
    taxon_pft_lookup$pft[i] = "???"  # "deciduous or evergreen shrub or tree"
    taxon_pft_lookup$commonName[i] = "sweetleaf"}

  else if(genusSpecies == "Taxus brevifolia"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "Pacific yew"}

  else if(genusSpecies == "Triadica sebifera"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "Chinese tallow"}

  else if(genusSpecies == "Tsuga heterophylla"){
    taxon_pft_lookup$pft[i] = "coniferous_forest"
    taxon_pft_lookup$commonName[i] = "western hemlock"}

  else if(genusSpecies == "Ulmus alata"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "winged elm"}

  else if(genusSpecies == "Ulmus americana"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "American elm"}

  else if(genusSpecies == "Ulmus rubra"){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "slippery elm"}

  else if(genusSpecies == "Ulmus sp."){
    taxon_pft_lookup$pft[i] = "deciduous_forest"
    taxon_pft_lookup$commonName[i] = "elm"}

@@

  else if(genusSpecies == "Zinnia acerosa"){
    taxon_pft_lookup$pft[i] = "???" # forb/herb, subshrub - grass_herb?
    taxon_pft_lookup$commonName[i] = "desert zinnia"}

  # For taxons not described in this code, set their PFT to unknown
  else print("PFT unknown")
